Paper_Figure

### 2023-10-27 paper_figure.Rmd
cellmarkerdb_change

# Fig - the AUROC given the rank and the ground truth
```{r}
library("RColorBrewer")
library("dplyr")
library("ggplot2")
path = "./benchmark_result/"
tissue_name = "marrow_facs"

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method_ls = colnames(df_benchmark)
method_fullname = setNames(c("LMD","singleCellHaystack","Hotspot","Marcopolo","SEMITONES","Seurat v3 default", "Seurat v3 Wilcoxon unfiltered","HighlyVariableGenes"),method_ls)
coldef = setNames(
  colorRampPalette(brewer.pal(9, "Set1"))(length(method_fullname)),
  method_fullname)
```
```{r}
df_auc <- read.table(paste0(path,tissue_name,"_auroc.csv"),header = TRUE)
df_auc = df_auc %>% filter(gt_set %in% c("Top100","CellMarkerDB")) %>% filter(!Method %in% "HighlyVariableGenes")
df_auc$Method <- with(df_auc, reorder(Method, -AUROC, FUN = median))
df_auc$gt_set <- factor(df_auc$gt_set,levels = c("Top100","CellMarkerDB"))
levels(df_auc$gt_set) = c("Criterion1 - MaxFC", "Criterion2 - CellMarkerDB")

# Create the plot
fig <- ggplot(df_auc, aes(x = gt_set, y = AUROC, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(AUROC, 2)), position = position_dodge(width = 0.85), vjust = -0.25, size = 2) +
  theme_minimal() +
  labs(x = "Ground-Truth Genesets", y = "AUROC", fill = "Method") + coord_cartesian(ylim = c(0.5, 1)) +
  theme(legend.position = "bottom")  +  scale_fill_manual(values= coldef[names(coldef)%in%df_auc$Method])
fig + ggtitle(tissue_name)
```

@@

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method_vs = "lmd"
method_vs_set = c("wilcox_default","hotspot","marcopolo","semi","haystack")
```
```{r}
sub = do.call(c,lapply(method_vs_set,function(method){
  sub = c(which(df_benchmark[,method] <= 100 & df_benchmark[,method_vs] > 500),
          which(df_benchmark[,method] > 500 & df_benchmark[,method_vs] <= 100) )
  sub
}))
df_label_all = df_benchmark[unique(sub),c(method_vs,method_vs_set)]
df_label_all$'legend' = sapply(seq(nrow(df_label_all)),function(i){
  paste(paste(method_fullname[colnames(df_label_all)],df_label_all[i,],sep = ":"),collapse = "\n")
})
g = c("Mogat2","Vpreb2","Cd19","Abca13","Il2rb","Mup3","Fyb","Naaa","Zf12","Phgdh")
pl = lapply(g,function(x){
  FeaturePlot(tiss,features = x,order =TRUE) + annotation_custom(grob = grid::textGrob(df_label_all[x,"legend"], x = 1, y = 1, just = c("right", "top"),gp = grid::gpar(col = "red", fontsize = 10)))
})
fig = cowplot::plot_grid(plotlist = pl,ncol = length(method_vs_set))
fig
```
```{r}
pl_rank = lapply(method_vs_set,function(method){
  df_label = data.frame(df_benchmark[,c(method,method_vs)],label = rownames(df_benchmark))
  df_label[c(which(df_label[,method] <= 100 & df_label[,method_vs] > 500)),"color"] = sprintf("Favor by %s (rank <= 100)",method)
  df_label[c(which(df_label[,method] > 500 & df_label[,method_vs] <= 100) ),"color"] = sprintf("Favor by %s (rank <= 100)",method_vs)
  df_label$'color' = as.factor(df_label$'color')
  p = ggplot(df_label, aes(x=!!as.name(method), y=!!as.name(method_vs),color = color)) + geom_point(size = 1) + 
  scale_color_manual(values = c("red", "blue", "grey50"),
                     breaks = levels(df_label$'color')) + 
    geom_abline(intercept = 0, slope = 1, col = "grey", linetype = "dashed") + scale_x_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    scale_y_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    expand_limits(x = c(1, 10^4), y = c(1, 10^4)) +
    labs(x = paste0(method_fullname[method]," Rank"), y = paste0(method_fullname[method_vs]," Rank"), color = "Highlighted Genes") + theme_minimal() 
  # annotate gene labels
  # library(ggrepel)
  p = p + geom_text(data = df_label %>% filter(!is.na(color)) %>% filter(label %in% g), aes(label=label))
  p
})
fig = cowplot::plot_grid(plotlist = pl_rank, ncol = length(method_vs_set))
fig
```

# Fig - Gene Co-localization Module Benchmark
```{r}
library(cowplot)
library(patchwork)
source("./LMD_function.R", echo = F)

path = "./benchmark_result/"
tissue_name = "marrow_facs"

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method = "lmd"
topn = 2000
# Gene prioritized by lmd
pl1 = lapply(c("wilcox_default","haystack","hotspot","hvg"),function(method_vs){
  local_gene = setdiff(rownames(df_benchmark)[order(df_benchmark[,method_vs])][1:topn], rownames(df_benchmark)[order(df_benchmark[,method])][1:topn])

  ## Gene-gene distance(similarity)---------
  distance_method = "jaccard"
  clustering_method = "average"
  dist = Calculate_distance(dat_alra[local_gene,], method = distance_method)

  gene_hree = hclust(dist, method = clustering_method)
  gene_partition = cutree(gene_hree,k=5)
  names(gene_partition) = labels(dist)

  top5 <- names(sort(table(gene_partition),decreasing = TRUE))[1:5]
  annotation_df = data.frame(Module = gene_partition)
  ann_colors = list(
    Module = c(setNames(colorRampPalette(brewer.pal(9, "Set1"))(5),1:5)))

  p_heatmap = pheatmap(as.matrix(dist),
                annotation_col = annotation_df,
                cluster_rows = gene_hree,
                cluster_cols = gene_hree,
                treeheight_row = 0,
                annotation_colors = ann_colors, 
                col=colorRampPalette(c("red","white","blue4"))(99),
                show_colnames = FALSE,
                show_rownames = FALSE,
                annotation_legend = TRUE,
                silent = TRUE)
  pl_module = FeaturePlot_meta(dat,visual_space,gene_partition)
  legend <- get_legend(pl_module[[1]])
  prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = ceiling(length(pl_module)/2))

  as.ggplot(p_heatmap) + cowplot::plot_grid(prow, legend, rel_widths = c(ceiling(length(pl_module)/2), .2)) + plot_annotation(title = sprintf("Genes in top 2000 by %s but not by %s (N = %d)",method_fullname[method_vs],method_fullname[method],length(local_gene))) + plot_layout(ncol = 2, widths = c(2, 3))
})
# The other way around
pl2 = lapply(c("wilcox_default","haystack","hotspot","hvg"),function(method_vs){
  local_gene = setdiff(rownames(df_benchmark)[order(df_benchmark[,method])][1:topn], rownames(df_benchmark)[order(df_benchmark[,method_vs])][1:topn])

  ## Gene-gene distance(similarity)---------
  distance_method = "jaccard"
  clustering_method = "average"
  dist = Calculate_distance(dat_alra[local_gene,], method = distance_method)

  gene_hree = hclust(dist, method = clustering_method)
  gene_partition = cutree(gene_hree,k=5)
  names(gene_partition) = labels(dist)

  top5 <- names(sort(table(gene_partition),decreasing = TRUE))[1:5]
  annotation_df = data.frame(Module = gene_partition)
  ann_colors = list(
    Module = c(setNames(colorRampPalette(brewer.pal(9, "Set1"))(5),1:5)))

  p_heatmap = pheatmap(as.matrix(dist),
                annotation_col = annotation_df,
                cluster_rows = gene_hree,
                cluster_cols = gene_hree,
                treeheight_row = 0,
                annotation_colors = ann_colors, 
                col=colorRampPalette(c("red","white","blue4"))(99),
                show_colnames = FALSE,
                show_rownames = FALSE,
                annotation_legend = TRUE,
                silent = TRUE)
  pl_module = FeaturePlot_meta(dat,visual_space,gene_partition)
  legend <- get_legend(pl_module[[1]])
  prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = ceiling(length(pl_module)/2))

  as.ggplot(p_heatmap) + cowplot::plot_grid(prow, legend, rel_widths = c(ceiling(length(pl_module)/2), .2)) + plot_annotation(title = sprintf("Genes in top 2000 by %s but not by %s (N = %d)",method_fullname[method],method_fullname[method_vs],length(local_gene))) + plot_layout(ncol = 2, widths = c(2, 3))
})

pdf(width = 12.5,height = 5)
pl1
dev.off()

pdf(width = 12.5,height = 5)
pl2
dev.off()
```

@@

fig = ggplot(score_measure %>% filter(Method!="all genes"), aes(x = TopGene, y = DensityIndex, color = Method, group = Method)) + geom_line() + scale_color_manual(values= coldef[names(coldef)%in%score_measure$Method]) + geom_hline(yintercept = baseline, linetype = "dashed", color = "grey1", alpha = 0.6) + annotate("text", x = max_x, y = baseline, label = "All_genes", vjust = -1, color = "grey1")  + theme_minimal()
fig
```

@@

# Fig - Module HeatMap
```{r}
load("./marrow_result/module_result.rdata")
source("./LMD_function.R", echo = F)
library(RColorBrewer)
library(dplyr)
module_color = setNames(colorRampPalette(brewer.pal(12, "Paired"))(nlevels(gene_partition)),levels(gene_partition))
celltype_color = setNames(colorRampPalette(brewer.pal(9, "Set1"))(length(unique(cell_label))),unique(cell_label))

p = pheatmap(as.matrix(dist),
              annotation_col = data.frame(Module = gene_partition),
              cluster_rows = gene_hree, 
              cluster_cols = gene_hree,
              ann_colors = list(Module = module_color),
              treeheight_row = 0,
              col=colorRampPalette(c("red","white","blue4"))(99),
              show_colnames = FALSE, 
              show_rownames = FALSE,
              annotation_legend = FALSE,
              # main = paste(distance_method,
              #              clustering_method,sep = "-"),
              silent = TRUE)
as.ggplot(p)
```
# Fig - Module Jaccard
```{r}
# Heatmap
pheatmap(jaccard_index, 
         cluster_rows=FALSE, cluster_cols=FALSE, 
         scale = "none", 
         color = colorRampPalette(rev(c("firebrick3", "white", "navy")))(100))
```
```{r}
# Bipartite Plot
jaccard_thred = 0.4

library(igraph)
library("grid") 
library("gridExtra")

df_edge <- as.data.frame(as.table(jaccard_index))
colnames(df_edge) = c("from","to","weight")
df_edge <- subset(df_edge, weight > jaccard_thred)
df_edge$width = ifelse(df_edge$weight > 0.8,2,0.5)
df_node = data.frame(name=c(names(module_color),names(celltype_color)),color = c(module_color,celltype_color))
df_node$type = ifelse(df_node$name %in% names(module_color),TRUE,FALSE)

# Define specific color for module
rownames(df_node) = df_node$name
ct_module = names(which(apply(jaccard_index,2,max) > jaccard_thred))
ct_subtype_module = c(4,5,6,30,39,42,43)
ct_multype_module = c(2,13,19,33,36,54)
cc_module = c(16,17,18,31)
df_node[names(module_color),"color"] = "grey"
df_node[ct_module,"color"] = "red"
df_node[ct_multype_module,"color"] = "purple"
df_node[ct_subtype_module,"color"] = "yellow"
df_node[cc_module,"color"] = "green"

g <- graph_from_data_frame(df_edge, directed=FALSE, vertices=df_node)
V(g)$shape <- ifelse(V(g)$type, "circle", "square")
E(g)$color <- ifelse(E(g)$weight > 0.8, "red", "grey")
l <- layout_as_bipartite(g, types=!V(g)$type)

plot(g, layout=l, vertex.size=2, vertex.label=ifelse(V(g)$type, V(g)$name, NA), vertex.frame.color = NA, asp=0.2, 
     vertex.label.cex=0.5,
     vertex.label.dist=-1,
     vertex.label.degree=pi/2)

# Create Node Legend & Edge Legend
color_label = c("green" = "cell cycle",purple = "multi cell type",red = "cell type",yellow = "cell subtype")
df_node$subtype = color_label[df_node$color]

p <- ggplot(df_node %>% filter(type), aes(x = 0, y = 0,color = subtype)) + geom_point(size = 7) + scale_color_manual(values= setNames(names(color_label),color_label)) + theme_minimal() + labs(color = "Module Type") + theme(legend.direction="horizontal")
grid.newpage()
grid.draw(get_legend(p))

p <- ggplot(df_node %>% filter(!type), aes(x = 0, y = 0,color = name)) + geom_point(size = 7,shape = 15) + scale_color_manual(values= df_node %>% filter(!type) %>% pull(color,name)) + theme_minimal() + labs(color = "Cell Type") + theme(legend.direction="horizontal")
grid.newpage()
grid.draw(get_legend(p))
```
# Fig - Module TSNE
```{r}
pl_module = lapply(levels(gene_partition),function(module){
  FeaturePlot_custom(value = cell_block[,module], coord = visual_space, value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module)))
})
names(pl_module) = levels(gene_partition)
legend <- get_legend(pl_module[[1]])
prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = 10)
pdf(width = 30, height = 18)
cowplot::plot_grid(prow, legend, rel_widths = c(10, .2))
dev.off()
```
# Fig - Module-CellType
```{r}
jaccard_thred = 0.4
one_hot_matrix <- sapply(unique(cell_label), function(x) as.integer(cell_label == x))
# Get CellType One-hot plot
pl_ct = lapply(colnames(one_hot_matrix),function(ct){
  FeaturePlot_custom(value = as.factor(one_hot_matrix[,ct]), coord = visual_space, value_name = "Indicator",title_name = ct)
})
names(pl_ct) = colnames(one_hot_matrix)

pl <- lapply(rownames(jaccard_index)[rev(order(apply(jaccard_index,1,max)))], function(celltype){
  if(max(jaccard_index[celltype,]) > jaccard_thred){
    p1 = pl_ct[[celltype]]
    module_name = colnames(jaccard_index)[which.max(jaccard_index[celltype,])]
    p2 = pl_module[[module_name]]
    p = as.ggplot(p1) + as.ggplot(p2) + plot_annotation(paste0("Jaccard Index: ",round(jaccard_index[celltype,module_name],2)))
    p
  }
})
sub = unlist(lapply(pl,function(x)is.null(x)))
pl = pl[-which(sub)]
pdf(width = 15, height = 20)
cowplot::plot_grid(plotlist = pl,ncol = 3)
dev.off()
```

>>>>

# Fig - the AUROC given the rank and the ground truth
```{r}
library("RColorBrewer")
library("dplyr")
library("ggplot2")

# Set the color code for all methods
method_ls = c("lmd","haystack","hotspot","marcopolo","semi","wilcox_default","wilcox_no_filter","hvg")
method_fullname = setNames(c("LMD","singleCellHaystack","Hotspot","Marcopolo","SEMITONES","Seurat v3 default", "Seurat v3 Wilcoxon unfiltered","HighlyVariableGenes"),method_ls)
coldef = setNames(
  colorRampPalette(brewer.pal(9, "Set1"))(length(method_fullname)),
  method_fullname)
```
```{r}
path = "./benchmark_result/"
tissue_ls = c("marrow_facs","pancreas_facs","lung_facs")
df_auc = do.call(rbind,lapply(tissue_ls,function(tissue_name){df = read.table(paste0(path,tissue_name,"_auroc.csv"),header = TRUE); df$'Tissue' = tissue_name; df}))

df_auc = df_auc %>% filter(gt_set %in% c("Top100","CellMarkerDB")) %>% filter(!Method %in% "HighlyVariableGenes")
df_auc$Method <- with(df_auc, reorder(Method, -AUROC, FUN = median))
df_auc$gt_set <- factor(df_auc$gt_set,levels = c("CellMarkerDB","Top100"))
levels(df_auc$gt_set) = c("Criterion1 - CellMarkerDB","Criterion2 - MaxFC")
df_auc$Tissue = factor(df_auc$Tissue,levels = tissue_ls)
levels(df_auc$Tissue) = c("Bone Marrow","Pancreas","Lung")
# Create the plot
fig <- ggplot(df_auc, aes(x = Tissue, y = AUROC, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(AUROC, 2)), position = position_dodge(width = 0.85), vjust = -0.25, size = 2) +
  theme_minimal() +
  labs(x = "Tissue", y = "AUROC", fill = "Method") + coord_cartesian(ylim = c(0.5, 1)) +
  theme(legend.position = "bottom")  +  scale_fill_manual(values= coldef[names(coldef)%in%df_auc$Method]) + facet_wrap(~gt_set)

ggsave(filename = "fig-known_marker_comparison.png", plot = fig, width = 10, height = 5)
```

@@

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method_vs = "lmd"
method_vs_set = c("wilcox_default","hotspot","marcopolo","semi","haystack")
```
```{r}
sub = do.call(c,lapply(method_vs_set,function(method){
  sub = c(which(df_benchmark[,method] <= 100 & df_benchmark[,method_vs] > 500),
          which(df_benchmark[,method] > 500 & df_benchmark[,method_vs] <= 100) )
  sub
}))
df_label_all = df_benchmark[unique(sub),c(method_vs,method_vs_set)]
df_label_all$'legend' = sapply(seq(nrow(df_label_all)),function(i){
  paste(paste(method_fullname[colnames(df_label_all)],df_label_all[i,],sep = ":"),collapse = "\n")
})
g = c("Cd19","Naaa","Mogat2","Tifa","Abca13","Zf12","Il2rb","Phgdh","Vpreb2","Fyb")
pl = lapply(g,function(x){
  FeaturePlot(tiss,features = x,order =TRUE) + annotation_custom(grob = grid::textGrob(df_label_all[x,"legend"], x = 1, y = 1, just = c("right", "top"),gp = grid::gpar(col = "red", fontsize = 10)))
})
fig = cowplot::plot_grid(plotlist = pl[as.numeric(t(matrix(1:length(pl),nrow = 2)))],ncol = length(method_vs_set))
ggsave(filename = "fig-ranking_comparison.png", plot = fig, width = 25, height = 10)
```
```{r}
pl_rank = lapply(method_vs_set,function(method){
  df_label = data.frame(df_benchmark[,c(method,method_vs)],label = rownames(df_benchmark))
  df_label[c(which(df_label[,method] <= 100 & df_label[,method_vs] > 500)),"color"] = sprintf("Favor by %s (rank <= 100)",method)
  df_label[c(which(df_label[,method] > 500 & df_label[,method_vs] <= 100) ),"color"] = sprintf("Favor by %s (rank <= 100)",method_vs)
  df_label$'color' = as.factor(df_label$'color')
  p = ggplot(df_label, aes(x=!!as.name(method), y=!!as.name(method_vs),color = color)) + geom_point(size = 1) + 
  scale_color_manual(values = c("red", "blue", "grey50"),
                     breaks = levels(df_label$'color')) + 
    geom_abline(intercept = 0, slope = 1, col = "grey", linetype = "dashed") + scale_x_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    scale_y_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    expand_limits(x = c(1, 10^4), y = c(1, 10^4)) +
    labs(x = paste0(method_fullname[method]," Rank"), y = paste0(method_fullname[method_vs]," Rank"), color = "Highlighted Genes") + theme_minimal() 
  # annotate gene labels
  # library(ggrepel)
  p = p + geom_text_repel(data = df_label %>% filter(!is.na(color)) %>% filter(label %in% g), aes(label=label),min.segment.length = unit(0, 'lines'),nudge_y = -0.5)
  p
})
pdf(width = 25,height = 5)
legend = get_legend(pl_rank[[1]] +  guides(color=guide_legend(direction="horizontal")))
prow = plot_grid(plotlist = lapply(pl_rank,function(x) x + NoLegend()), ncol = length(method_vs_set))
plot_grid(prow, legend, ncol = 1, rel_heights = c(1, .2))
dev.off()
```

<!-- # Fig - Gene Co-localization Module Benchmark -->
<!-- ```{r} -->
<!-- library(cowplot) -->
<!-- library(patchwork) -->
<!-- source("./LMD_function.R", echo = F) -->

<!-- path = "./benchmark_result/" -->
<!-- tissue_name = "marrow_facs" -->

<!-- df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv")) -->
<!-- method = "lmd" -->
<!-- topn = 2000 -->
<!-- # Gene prioritized by lmd -->
<!-- pl1 = lapply(c("wilcox_default","haystack","hotspot","hvg"),function(method_vs){ -->
<!--   local_gene = setdiff(rownames(df_benchmark)[order(df_benchmark[,method_vs])][1:topn], rownames(df_benchmark)[order(df_benchmark[,method])][1:topn]) -->

<!--   ## Gene-gene distance(similarity)--------- -->
<!--   distance_method = "jaccard" -->
<!--   clustering_method = "average" -->
<!--   dist = Calculate_distance(dat_alra[local_gene,], method = distance_method) -->

<!--   gene_hree = hclust(dist, method = clustering_method) -->
<!--   gene_partition = cutree(gene_hree,k=5) -->
<!--   names(gene_partition) = labels(dist) -->

<!--   top5 <- names(sort(table(gene_partition),decreasing = TRUE))[1:5] -->
<!--   annotation_df = data.frame(Module = gene_partition) -->
<!--   ann_colors = list( -->
<!--     Module = c(setNames(colorRampPalette(brewer.pal(9, "Set1"))(5),1:5))) -->

<!--   p_heatmap = pheatmap(as.matrix(dist), -->
<!--                 annotation_col = annotation_df, -->
<!--                 cluster_rows = gene_hree, -->
<!--                 cluster_cols = gene_hree, -->
<!--                 treeheight_row = 0, -->
<!--                 annotation_colors = ann_colors,  -->
<!--                 col=colorRampPalette(c("red","white","blue4"))(99), -->
<!--                 show_colnames = FALSE, -->
<!--                 show_rownames = FALSE, -->
<!--                 annotation_legend = TRUE, -->
<!--                 silent = TRUE) -->
<!--   pl_module = FeaturePlot_meta(dat,visual_space,gene_partition) -->
<!--   legend <- get_legend(pl_module[[1]]) -->
<!--   prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = ceiling(length(pl_module)/2)) -->

<!--   as.ggplot(p_heatmap) + cowplot::plot_grid(prow, legend, rel_widths = c(ceiling(length(pl_module)/2), .2)) + plot_annotation(title = sprintf("Genes in top 2000 by %s but not by %s (N = %d)",method_fullname[method_vs],method_fullname[method],length(local_gene))) + plot_layout(ncol = 2, widths = c(2, 3)) -->
<!-- }) -->
<!-- # The other way around -->
<!-- pl2 = lapply(c("wilcox_default","haystack","hotspot","hvg"),function(method_vs){ -->
<!--   local_gene = setdiff(rownames(df_benchmark)[order(df_benchmark[,method])][1:topn], rownames(df_benchmark)[order(df_benchmark[,method_vs])][1:topn]) -->

<!--   ## Gene-gene distance(similarity)--------- -->
<!--   distance_method = "jaccard" -->
<!--   clustering_method = "average" -->
<!--   dist = Calculate_distance(dat_alra[local_gene,], method = distance_method) -->

<!--   gene_hree = hclust(dist, method = clustering_method) -->
<!--   gene_partition = cutree(gene_hree,k=5) -->
<!--   names(gene_partition) = labels(dist) -->

<!--   top5 <- names(sort(table(gene_partition),decreasing = TRUE))[1:5] -->
<!--   annotation_df = data.frame(Module = gene_partition) -->
<!--   ann_colors = list( -->
<!--     Module = c(setNames(colorRampPalette(brewer.pal(9, "Set1"))(5),1:5))) -->

<!--   p_heatmap = pheatmap(as.matrix(dist), -->
<!--                 annotation_col = annotation_df, -->
<!--                 cluster_rows = gene_hree, -->
<!--                 cluster_cols = gene_hree, -->
<!--                 treeheight_row = 0, -->
<!--                 annotation_colors = ann_colors,  -->
<!--                 col=colorRampPalette(c("red","white","blue4"))(99), -->
<!--                 show_colnames = FALSE, -->
<!--                 show_rownames = FALSE, -->
<!--                 annotation_legend = TRUE, -->
<!--                 silent = TRUE) -->
<!--   pl_module = FeaturePlot_meta(dat,visual_space,gene_partition) -->
<!--   legend <- get_legend(pl_module[[1]]) -->
<!--   prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = ceiling(length(pl_module)/2)) -->

<!--   as.ggplot(p_heatmap) + cowplot::plot_grid(prow, legend, rel_widths = c(ceiling(length(pl_module)/2), .2)) + plot_annotation(title = sprintf("Genes in top 2000 by %s but not by %s (N = %d)",method_fullname[method],method_fullname[method_vs],length(local_gene))) + plot_layout(ncol = 2, widths = c(2, 3)) -->
<!-- }) -->

<!-- pdf(width = 12.5,height = 5) -->
<!-- pl1 -->
<!-- dev.off() -->

<!-- pdf(width = 12.5,height = 5) -->
<!-- pl2 -->
<!-- dev.off() -->
<!-- ``` -->

@@

fig = ggplot(score_measure %>% filter(Method!="all genes"), aes(x = TopGene, y = DensityIndex, color = Method, group = Method)) + geom_line(aes(linetype = Method)) + guides(linetype="none") + scale_color_manual(values= coldef[names(coldef)%in%score_measure$Method]) + geom_hline(yintercept = baseline, linetype = "dashed", color = "grey1", alpha = 0.6) + annotate("text", x = max_x, y = baseline, label = "All_genes", vjust = -1, color = "grey1")  + theme_minimal() + geom_text_repel(data = score_measure %>%  filter(Method!="all genes") %>% group_by(Method) %>% slice_head(n = 2) %>% slice_tail(n = 1), aes(label = Method), hjust = 0)
pdf(width = 8,height = 5)
fig
dev.off()
```

@@

# Fig - Gene-Gene Colocolization HeatMap
```{r}
load("./marrow_result/module_result.rdata")
source("./LMD_function.R", echo = F)
library(RColorBrewer)
library(dplyr)
module_color = setNames(colorRampPalette(brewer.pal(12, "Paired"))(nlevels(gene_partition)),levels(gene_partition))
celltype_color = setNames(colorRampPalette(brewer.pal(9, "Set1"))(length(unique(cell_label))),unique(cell_label))

p = pheatmap(as.matrix(dist),
              annotation_col = data.frame(Module = gene_partition),
              cluster_rows = gene_hree, 
              cluster_cols = gene_hree,
              ann_colors = list(Module = module_color),
              treeheight_row = 0,
              col=colorRampPalette(c("firebrick3", "white"))(99),
              show_colnames = FALSE, 
              show_rownames = FALSE,
              annotation_legend = FALSE,
              # main = paste(distance_method,
              #              clustering_method,sep = "-"),
              silent = TRUE)
p = as.ggplot(p)
ggsave(filename = "fig-moduleheatmap.png", plot = p, width = 10, height = 10)
```
# Fig - Module Jaccard
```{r}
jaccard_index_pruned = jaccard_index[apply(jaccard_index,1,max) > 0.4,]
jaccard_index_pruned = jaccard_index_pruned[,apply(jaccard_index_pruned,2,max) > 0.4]

colnames(jaccard_index_pruned) = paste0("M",colnames(jaccard_index_pruned))
p = pheatmap(t(jaccard_index_pruned)[,names(sort(apply(jaccard_index_pruned,1,which.max)))],
         cluster_rows=FALSE, cluster_cols=FALSE, 
         scale = "none", 
         color = colorRampPalette(rev(c("firebrick3", "white")))(99),
         angle_col = 45,legend_title = "Jaccard Index",silent = TRUE,
         cellwidth = 15, cellheight = 10)
p = as.ggplot(p)
ggsave(filename = "jaccard_heatmap.png", plot = p, width = 5, height = 10)
```
```{r}
# # Bipartite Plot
# jaccard_thred = 0.4
# 
# library(igraph)
# library("grid") 
# library("gridExtra") 
# 
# df_edge <- as.data.frame(as.table(jaccard_index))
# colnames(df_edge) = c("from","to","weight")
# df_edge <- subset(df_edge, weight > jaccard_thred)
# df_edge$width = ifelse(df_edge$weight > 0.8,2,0.5)
# df_node = data.frame(name=c(names(module_color),names(celltype_color)),color = c(module_color,celltype_color))
# df_node$type = ifelse(df_node$name %in% names(module_color),TRUE,FALSE)
# 
# # Define specific color for module
# rownames(df_node) = df_node$name
# ct_module = names(which(apply(jaccard_index,2,max) > jaccard_thred))
# ct_subtype_module = c(4,5,6,30,39,42,43)
# ct_multype_module = c(2,13,19,33,36,54)
# cc_module = c(16,17,18,31)
# df_node[names(module_color),"color"] = "grey"
# df_node[ct_module,"color"] = "red"
# df_node[ct_multype_module,"color"] = "purple"
# df_node[ct_subtype_module,"color"] = "yellow"
# df_node[cc_module,"color"] = "green"
# 
# g <- graph_from_data_frame(df_edge, directed=FALSE, vertices=df_node)
# V(g)$shape <- ifelse(V(g)$type, "circle", "square")
# E(g)$color <- ifelse(E(g)$weight > 0.8, "red", "grey")
# l <- layout_as_bipartite(g, types=!V(g)$type)
# 
# plot(g, layout=l, vertex.size=2, vertex.label=ifelse(V(g)$type, V(g)$name, NA), vertex.frame.color = NA, asp=0.2, 
#      vertex.label.cex=0.5,
#      vertex.label.dist=-1,
#      vertex.label.degree=pi/2)
# 
# # Create Node Legend & Edge Legend
# color_label = c("green" = "cell cycle",purple = "multi cell type",red = "cell type",yellow = "cell subtype")
# df_node$subtype = color_label[df_node$color]
# 
# p <- ggplot(df_node %>% filter(type), aes(x = 0, y = 0,color = subtype)) + geom_point(size = 7) + scale_color_manual(values= setNames(names(color_label),color_label)) + theme_minimal() + labs(color = "Module Type") + theme(legend.direction="horizontal")
# grid.newpage()
# grid.draw(get_legend(p))
# 
# p <- ggplot(df_node %>% filter(!type), aes(x = 0, y = 0,color = name)) + geom_point(size = 7,shape = 15) + scale_color_manual(values= df_node %>% filter(!type) %>% pull(color,name)) + theme_minimal() + labs(color = "Cell Type") + theme(legend.direction="horizontal")
# grid.newpage()
# grid.draw(get_legend(p))
```
# Fig - Module TSNE
```{r}
pl_module = lapply(levels(gene_partition),function(module){
  FeaturePlot_custom(value = cell_block[,module], coord = visual_space, value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module))) + scale_color_gradient(limits = c(0, 1),low = "lightgrey", high = "blue")
})
names(pl_module) = levels(gene_partition)
legend_module <- get_legend(pl_module[[1]])
prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = 10)
p = cowplot::plot_grid(prow, legend_module, rel_widths = c(10, 1))
ggsave(filename = "fig-moduletsne.png", plot = p, width = 30, height = 18)
```
